Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-07-02 manuscript/phylogenetic_signal_manuscript.tex
some very small corrections, updated word count

Main text: 4522

\begin{itemize}
  \item Introduction: 805 
  \item Materials and Methods: 1831 
  \item Results: 665
  \item Discussion: 1139 
  \item Acknowledgements: 83
\end{itemize}

@@

    \item We introduce a novel approach with which to quantify
          overlap of interaction
          partners for each pair of plants in 59 pollination and 11 herbivory
          networks.  We then tested for relationships between phylogenetic 
          distance and partner overlap within each network, and whether these 
          relationships varied with the composition of the plant community.
          Finally, we tested for different relationships within well-represented
          plant families.

@@

\section*{Warning}

Our original methodology was different from that in Fontaine \& Th\'{e}bault 2015 (Popul Ecol), but now that we've switched to Jaccard as our overlap measure we're doing almost the exact same thing with a slightly different set of networks. This will probably make it quite hard to argue novelty.

\textbf{DBS: }

@@

\end{spacing}
\begin{spacing}{1.5}

@@

@@

    We then estimated phylogenetic distances between the remaining species. To accomplish 
    this, we constructed a phylogenetic tree for our dataset based on a dated
    `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
    in the angiosperm mega-tree (largely ferns and tree ferns). For angiosperms,
    a sister taxon was identified using~\citet{APW} and the species added manually.
    Ferns, tree ferns, and a single club moss were added to the base of the tree.
    This means that closely-related non-angiosperm species appear to have very long 
    phylogenetic distances between them. For this reason, we excluded comparisons 
    between pairs of non-angiosperms from our subsequent analyses. As only two networks (both 
    herbivory networks) included more than one such species and non-angiosperms
    were always a small minority of any network, we do not 
    believe that omitting these comparisons has greatly affected our results.
    To obtain trees for each network, we 
    pruned the dated mega-tree to include only species in that network.

@@

    Models for two families did not converge. In both the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} in herbivory networks (represented by five species in one network), one pair of species shared a single interaction partner while all other pairs did not share any interaction partners. The model for \emph{Sapindaceae} in pollination networks did converge.

>>>>

Main text: 5612 % Limit 6,500

\begin{itemize}
  \item Introduction: 1074
  \item Materials and Methods: 2223 
  \item Results: 890
  \item Discussion: 1342
  \item Acknowledgements: 83
\end{itemize}

% Word counts updated July 2, include some comments.

@@

    \item We introduce a novel approach with which to quantify
          overlap of interaction
          partners for each pair of plants in 59 pollination and 11 herbivory
          networks based on the numbers of potential interaction partners which are shared and not shared.  We then tested for relationships between phylogenetic 
          distance and partner overlap within each network, and whether these 
          relationships varied with the composition of the plant community.
          Finally, we tested for different relationships within well-represented
          plant families.

@@

@@

\end{spacing}
\begin{spacing}{1.5}
% \clearpage

@@

% \clearpage

@@

    We then estimated phylogenetic distances between the remaining species. To accomplish 
    this, we constructed a phylogenetic tree for our dataset based on a dated
    `mega-tree' of angiosperms~\citep{Zanne2014}. Some species were not included
    in the angiosperm mega-tree. For angiosperms,
    a sister taxon was identified using~\citet{APW} and the species added manually.
    Ferns, tree ferns, and a single club moss were added to the base of the tree.
    This means that closely-related non-angiosperm species appear to have very long 
    phylogenetic distances between them. For this reason, we excluded comparisons 
    between pairs of non-angiosperms from our subsequent analyses. As only two networks (both 
    herbivory networks) included more than one such species and non-angiosperms
    were always a small minority of any network, we do not 
    believe that omitting these comparisons has greatly affected our results.
    To obtain trees for each network, we 
    pruned the dated mega-tree to include only species in that network.

@@

    Models for two families did not converge. In the \emph{Lauraceae}, (represented by four species in one pollination network) and the \emph{Sapindaceae} (represented by five species in one herbivory network and five species in two pollination networks), only one pair of species per network type shared any interaction partners while all other pais did not share any interaction partners.

% \clearpage
